|

### 2021-01-15 supplementary_information.Rmd
Edits: add tables to SI

---
title: |
  | Ecosystem size and complexity dictate riverine biodiversity
  | Supplementary Information for:
author:
- Akira Terui^[Department of Biology, University of North Carolina at Greensboro]
- Seoghyun Kim\footnotemark[1]
- Christine L. Dolph^[Department of Ecology, Evolution and Behavior, University of
  Minnesota]
- Taku Kadoya^[National Institute for Environmental Studies]
- Yusuke Miyazaki^[Shiraume Gakuen University]
output:
  pdf_document:
    toc: yes
    toc_depth: 2
bibliography: reference.bib
csl: nature.csl
---

@@

# Hokkaido data
dat_hkd <- read_csv(here::here('/empirical/data_org_hkd/data_fmt_hkd_latest.csv')) %>% 
  filter(Year >= 1990)

# Midwest data
fishdata <- list.files(path = here::here("/empirical/data_org_mw"), full.names = TRUE) %>% lapply(read_csv)
dat_mw <- do.call(what = bind_rows, args = fishdata)

@@

## Table S1 Species list in Hokkaido, Japan

Species list in Hokkaido, Japan. Species are ordered alphabetically.

@@

dat_hkd %>% 
  filter(Year >= 1990) %>% 
  mutate(Species = str_replace_all(str_to_title(OTU), "_", " ")) %>% 
  mutate(Species = str_replace_all(Species, "(spp$)|(spp\\s)", "spp\\.")) %>% 
  mutate(Species = str_replace_all(Species, "(sp$)", "sp\\.")) %>% 
  mutate(Species = str_replace_all(Species, "(subsp)", "subsp\\. ")) %>% 
  mutate(Species = str_replace_all(Species, "(sp\\sme$)", "sp\\. ME")) %>% 
  group_by(Species) %>% 
  summarise('Number of sites present' = n_distinct(SiteID)) %>% 
  kable(format = 'markdown')

>>>>

---
title: |
  | Supplementary Information for:
  | Ecosystem size and complexity dictate riverine biodiversity
author:
- Akira Terui^[Department of Biology, University of North Carolina at Greensboro]
- Seoghyun Kim\footnotemark[1]
- Christine L. Dolph^[Department of Ecology, Evolution and Behavior, University of
  Minnesota]
- Taku Kadoya^[National Institute for Environmental Studies]
- Yusuke Miyazaki^[Shiraume Gakuen University]
output:
  pdf_document:
    toc: yes
    toc_depth: 2
bibliography: reference.bib
csl: nature.csl
---

@@

# Hokkaido data
dat_hkd <- read_csv(here::here('/empirical/data_out/dat_hkd_site.csv'))

# Midwest data
dat_mw <- read_csv(here::here('/empirical/data_out/dat_mw_site.csv'))

@@

## Table S1 List of fish species in Hokkaido, Japan

List of fish species in Hokkaido, Japan that are included in our statistical analysis. `r n_distinct(dat_hkd$Species)` species are ordered alphabetically with the number of sites present and % occupancy out of `r n_distinct(dat_hkd$SiteID)` sites.

@@

dat_hkd %>% 
  mutate(n_site = n_distinct(SiteID)) %>% 
  mutate(Species = str_replace_all(str_to_title(Species), "_", " ")) %>% 
  mutate(Species = str_replace_all(Species, "(spp$)|(spp\\s)", "spp\\.")) %>% 
  mutate(Species = str_replace_all(Species, "(sp$)", "sp\\.")) %>% 
  mutate(Species = str_replace_all(Species, "(subsp)", "subsp\\. ")) %>% 
  mutate(Species = str_replace_all(Species, "(sp\\sme$)", "sp\\. ME")) %>% 
  group_by(Species) %>% 
  summarise('Number of sites present' = n_distinct(SiteID),
            'Occupancy (%)' = round((n_distinct(SiteID)*100)/unique(n_site), 2)) %>% 
  kable(format = 'markdown')

## Table S2 List of fish species in Midwest, US

List of fish species in Midwest, US that are included in our statistical analysis. `r n_distinct(dat_mw$Species)` species are ordered alphabetically with the number of sites present and % occupancy out of `r n_distinct(dat_mw$SiteID)` sites.

```{r chunk_table2}

sp_mw_latin <- read_csv(here::here('/empirical/data_out/data_mw_splist_latin.csv'))

dat_mw %>% 
  mutate(n_site = n_distinct(SiteID)) %>% 
  rename(Common_name = Species) %>% 
  group_by(Common_name) %>% 
  summarise('Number of sites present' = n_distinct(SiteID),
            'Occupancy (%)' = round((n_distinct(SiteID)*100)/unique(n_site), 2)) %>% 
  left_join(sp_mw_latin, by = "Common_name") %>% 
  select(Species = Latin_name,
         'Number of sites present',
         'Occupancy (%)') %>% 
  arrange(Species) %>% 
  kable(format = 'markdown')
